Automatic Extraction of JavaScript Formal Semantics from ECMAScript Specifications

### 2019-07-26 icse/parser.tex
Added BNF_ES explanation
Temporal updates for parsers

\subsection{Predictive Parsers vs Recursive Descent Parsers}
\begin{itemize}
  \item Predictive parser
    \begin{itemize}
      \item PROS: widely-used (Yacc), linear time, lookahead for predictions, no backtrack
      \item CONS: need to restructure CFG, not easy to implement ES-BNF features
    \end{itemize}
  \item Recursive descent parsers
    \begin{itemize}
      \item PROS: Scala-supported (Scala parser combinators), easily support ES-BNF features, no need to re-structure CFG
      \item CONS: PEG not CFG, exponential time for bactkracing.
    \end{itemize}
\end{itemize}

@@

\subsection{Generating Parsers for \( \text{BNF}_\text{ES} \)}
How to handle each \( \text{BNF}_\text{ES} \) features

>>>>

In this section, we introduce a way to automatically generate JavaScript parsers
from given ECMAScript specifications. First, we explain \( \bnfes \), an extension
of BNF used in ECMAScript to describe lexical and syntactic grammars of JavaScript.
We defined a recursive descent parser generator to support \( \bnfes \) notations.
We implemented our idea by extending the basic Scala parser combinator.
The implementation also support the automatic semicolon insertion,
one of the most distinct parsing feautres in ECMAScript.

\subsection{\( \bnfes \): Grammars for ECMAScripts}

ECMAScript supports their lexical and syntactic grammars based on
their own Backus-Naur form(BNF), we call it as \( \bnfes \).
It provides five additional notations:
\begin{itemize}
  \item \( \code{T}_\code{opt} \)
    - the (non-)terminal \( \term \) is optional
  \item \( \code{T but not T'} \):
    - the (non-)terminal \( \term \) should be not the (non-)terminal \( \code{T'} \)
  \item \( \code{[lookahead} = \code{T]} \)
    - it checks that remain inputs are possible to be parsed using \( \code{T} \)
    but does not consume any inputs.
  \item \( \code{[lookahead} \neq \code{T]} \)
    - it checks that remain inputs are not possible to be parsed using \( \code{T} \)
    but does not consume any inputs.
    % \code{T[P}^\code{*}\code{]} & \text{parameters}
    % \\\hline
    % \begin{itemize}
    %   \item \code{?P} & \text{passing argument} \code{P}
    %   \item \code{+P} & \kwtrue
    %   \item \code{\textasciitilde}\code{P} &  \kwfalse
    % \end{itemize}
    % \code{[+P] T} & \text{if} \; \code{P} \; \text{is} \; \kwtrue \;\text{, added} \; \code{T}
    % \\\hline
    % \code{[\textasciitilde}\code{P] T} & if  \code{P}  is  \kwfalse , added  \code{T}
    % \\\hline
\end{itemize}

Our goal is to automatically generate parsers from grammars written in \( \bnfes \).

% There are two different parsing approaches:
% ``top-down'' approach (LL-style parsing) and
% ``bottom-up'' approach (LR-style parsing).
% Top-down approach support 
% 
% There are two different kinds of parsers: top-down parsing, bottom-up parsing.
% 
% 
% 
% Such features could be easily represented in Parsing Expression Grammars (PEGs).
% 
% 
% 
% Backus–Naur form(BNF)에 다섯 가지의 방식을 추가한 형태로 lexical 및 syntactic grammar를 제공한다.
% 각각의

\subsection{Predictive Parsers vs Recursive Descent Parsers}

@@

\subsection{Generating Parsers for \( \bnfes \)}
How to handle each \( \bnfes \) features
% \begin{table}
%   \centering
%   \[
%     \begin{array}{l|l}
%       \bnfes & \peg
%       \\\hline
%       \code{T}_\code{opt} & \code{T?}
%       \\\hline
%       \code{T but not T'} & \code{-T'} \; \code{\textasciitilde} \; \code{T}
%       \\\hline
%       \code{[lookahead} = \code{T]} & \code{+T}
%       \\\hline
%       \code{[lookahead} \neq \code{T]} & \code{-T}
%       \\\hline
%       % \code{T[P}^\code{*}\code{]} & \text{parameters}
%       % \\\hline
%       % \begin{itemize}
%       %   \item \code{?P} & \text{passing argument} \code{P}
%       %   \item \code{+P} & \kwtrue
%       %   \item \code{\textasciitilde}\code{P} &  \kwfalse
%       % \end{itemize}
%       % \code{[+P] T} & \text{if} \; \code{P} \; \text{is} \; \kwtrue \;\text{, added} \; \code{T}
%       % \\\hline
%       % \code{[\textasciitilde}\code{P] T} & if  \code{P}  is  \kwfalse , added  \code{T}
%       % \\\hline
%     \end{array}
%   \]
%   \caption{Conversion from \( \bnfes \) into \( \peg \)}
%   \label{table:bnfes}
% \end{table}
